Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex

\begin{theorem} \label{thm:general-char}
  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
  Then $\ell$ is $d$-embeddable if and only if there exists a collection of polytopes $\T^r = \{T^r_y : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
  \begin{enumerate}
    \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L(\varphi(r))_y$ and for all $r \in \R$, we have $L(\varphi(r))_y = \ell(r)_y$.
  \end{enumerate}
\end{theorem}
\begin{proof}
  $(\implies)$ 
%  If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
%  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
%  Let $\Gamma$ be the property elicited by the surrogate $L$.
%  To see the optimality condition is satisfied, consider that for each $r \in \R$, we have $\gamma_r = \Gamma_{\varphi(r)}$ by Bayes Risks matching~\cite[Proposition 1]{finocchiaro2019embedding} and level sets of the property mapping to subgradients of the Bayes Risk by~\cite{frongillo2014general}.
%  In turn, we have $\Gamma_{\varphi(r)}= \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
%  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.  
$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma~\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
Monotonicity is simply a corollary of the embedding definition.

  $(\impliedby)$ The first two embedding conditions hold by the assumption of $\varphi$ in the monotonicity condition.
  Now consider that $\gamma_r = D(\T^r)$ by Optimality. 
  Taking $\T^r = \partial L(\varphi(r))_y$, Lemma~\ref{lem:minkowski-0-opt} implies that $D(\T^r) = \Gamma_{\varphi(r)}$, giving the third embedding characterization.
\end{proof}

>>>>

\begin{theorem} \label{thm:general-char}
  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
  Then $\ell$ is $d$-embeddable if and only if there exists a collection of polytopes $\T^r = \{T^r_y : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
  \begin{enumerate}
    \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L(\varphi(r))_y$ and for all $r \in \R$, we have $L(\varphi(r))_y = \ell(r)_y$.
  \end{enumerate}
\end{theorem}
\begin{proof}
  $(\implies)$ 
%  If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
%  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
%  Let $\Gamma$ be the property elicited by the surrogate $L$.
%  To see the optimality condition is satisfied, consider that for each $r \in \R$, we have $\gamma_r = \Gamma_{\varphi(r)}$ by Bayes Risks matching~\cite[Proposition 1]{finocchiaro2019embedding} and level sets of the property mapping to subgradients of the Bayes Risk by~\cite{frongillo2014general}.
%  In turn, we have $\Gamma_{\varphi(r)}= \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.
%  Clearly this set of polytopes $\T$ satisfies the monotonicity condition by the definition of $L$ embedding $\ell$.  
$L$ embeds $\ell$ implies $\gamma_{r} = \Gamma_\varphi(r) = D(\T^r)$ by Lemma~\ref{lem:minkowski-0-opt} for all $r \in \R$, thus we have optimality.
Monotonicity follows directly from the embedding definition.

  $(\impliedby)$ The first two embedding conditions hold by the assumption of $\varphi$ in the monotonicity condition.
  The third condition is $\gamma_r = \Gamma_{\varphi(r)}$ for all $r$.
  From optimality, we have $\gamma_r = D(\T^r)$.
  Taking $\T^r = \{T^r_y : y \in \Y\}$, Lemma~\ref{lem:minkowski-0-opt} implies that $\Gamma_{\varphi(r)} = D(\T^r) = \gamma_r$.
\end{proof}
